% LaTeX file for resume
% This file uses the resume document class (res.cls)



\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.7in
% adjust the top margin to better vertically center the page
\headheight= -0.65in
\pdfpagewidth=\paperwidth
\pdfpageheight=\paperheight
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\usepackage[normalem]{ulem}

\usepackage{hyperref}

\addtolength{\textheight}{0.4in} % use this if pdflatex outputs two pages with the first page blank

\begin{document}
\begin{minipage}{\textwidth}

\name{\hfil Jordan R. Horwich \hfil \\ \hfil \uline{\href{http://GitHub.com/VoidingWarranties}{GitHub.com/VoidingWarranties}} \hfil \\ \hfil Jordan@JordanHorwich.com \hfil \\ \hfil (207) 632-0713 \hfil \\ } % the \\[12pt] adds a blank line after name

\begin{resume}

\section{Professional Experience}
{\bf Software Engineer,} \uline{Google} \hfill January 2017 -- Present
 \begin{itemize} \itemsep -2pt % reduce space between items
 \item Currently working on \uline{\href{https://blog.google/products/search/introducing-knowledge-graph-things-not/}{Google Knowledge Graph}}, a part of Google Search.
 \item Developed horizontal tooling and infrastructure widely used throughout Search teams for ingestion and maintenance of data in the Knowledge Graph.
 \item Designed a UI and algorithm for performing arbitrary topological transformations on unsanitized structured data for the purpose of schema mapping.
 \end{itemize}



{\bf Software Engineer \& First Employee,} \uline{Nebulous Inc.} \hfill December 2015 -- December 2016
 \begin{itemize} \itemsep -2pt % reduce space between items
 \item Developed, marketed, and pitched Sia, a blockchain-based decentralized storage network.
 \item Improved Sia's initial blockchain download by a factor of 25,000.
 \item Secured the gateway that maintains Sia's decentralized peer-to-peer network to prevent against eclipse attacks.
 \item Finalized Sia's REST-like API in preparation for launching out of beta.
 \end{itemize}



{\bf Software Engineer Intern,} \uline{LinkedIn} \hfill Summer 2015
 \begin{itemize} \itemsep -2pt % reduce space between items
 \item Implemented company and school mini-profiles UI for LinkedIn's homepage using the Play Framework in Scala and Dust.js as well as permalink UI for feed updates.
 \end{itemize}



{\bf Software Engineer Intern,} \uline{Intentional Software} \hfill Spring 2015
 \begin{itemize} \itemsep -2pt % reduce space between items
 \item Designed and developed a natural user interface using the Microsoft Kinect to implement a gesture and virtual touch screen interface.
 \item Wrote a hand pose classifier in C++ using feature matching in OpenCV.
 \item Developed an N-dimensional implementation in C++ of UW's \$1 Recognizer for atomic gesture recognition with the Kinect. % TODO: add link to UW's $1 Recognizer
 \item Architected a data transformation pipeline for processing input from motion sensing devices such as the Kinect, Leap Motion, and Myo.
 \end{itemize}



{\bf Software Engineer Intern,} \uline{Bloomberg L.P.} \hfill Summer 2014
 \begin{itemize} \itemsep -2pt
 \item Designed and developed a Bloomberg Terminal application using C++ and service-oriented architecture on the back end and javascript on the front end. This tool was used to quickly fix a fatal error in the way market data from exchanges were stored. Similar errors previously took many hours to fix without my tool.
 \end{itemize}



{\bf Software Engineer \& Physics Consultant,} \uline{Mimir Physics} \hfill Summer 2012 -- 2013
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Co-author of a patent (pending application) for a hardware and software solution to account for variations in the spectra of multiple light sources in imaging applications.
 \item Developed an image processor in C++ for high color bit depth images that analyzed color data to create color images with an absolute color error of $\Delta E^* < 1$.
 \end{itemize}

\section{Skills}
\begin{tabular}{l l r}
		{\bf Languages:} & Go, C++, C & $>$ 5 years experience \\
		                 & Angular, Typescript, Python & 4 years experience \\
		                 & SQL, Swift, Scala & $<$ 3 years experience \\
\end{tabular} \\
\bgroup
\def\arraystretch{1.23} %adjust this number to adjust the spacing of the below table. Make sure to not make it so big that the resume overflows to 2 pages.
\begin{tabular}{l p{4in}}
		{\bf Software:} & Mercurial, Git, MacOS, Linux \\
 \end{tabular}
\egroup

\section{Other \\ Projects}
\begin{description}
	\item[Offsite APFS Backup] -- \uline{\href{https://GitHub.com/VoidingWarranties/offsite-apfs-backup}{GitHub.com/VoidingWarranties/Offsite-APFS-Backup}} \\
		A non-destructive incremental backup utility for cloning APFS snapshots.
	\item[MyoIntelligesture] -- \uline{\href{http://GitHub.com/VoidingWarranties/Myo-Intelligesture}{GitHub.com/VoidingWarranties/Myo-Intelligesture}} \\
		A library for processing raw data from the Thalmic Myo using a non-linear data pipeline.
	\item[MyoHome] -- \uline{\href{http://GitHub.com/VoidingWarranties/Myo-Home}{GitHub.com/VoidingWarranties/Myo-Home}} \\
		A natural user interface for home automation using the Thalmic Myo. Allows you to control home appliances by pointing at them and gesturing. Heavily uses MyoIntelligesture.
	\item[SignSight] -- \uline{\href{http://GitHub.com/VoidingWarranties/SignSight}{GitHub.com/VoidingWarranties/SignSight}} \\
		A unique computer vision approach to automatic traffic sign recognition.
\end{description}

\section{Education}
{\bf Rensselaer Polytechnic Institute}, Troy, NY \hfill 2012 -- 2015 \\
81\% of major requirements completed towards B.S., Computer Science \\
GPA: 3.72

\section{Courses}
\begin{tabular}{lll}
$\bullet$ Machine Learning & $\bullet$ Human-Computer Interaction Usability & $\bullet$ Algorithms \\
$\bullet$ Computer Graphics & $\bullet$ Natural Language Processing & $\bullet$ Data Structures \\
\end{tabular}

\end{resume}
\end{minipage}
\end{document}
